% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Yuchong Pan}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  Dong Xian Huan He Yan 11-2 \\
  Yuecheng District, Shaoxing \\
  Zhejiang Province, China 312000
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (86) 138-6752-7534 \\
    Email: & \href{mailto:panyuchong@gmail.com}{\tt panyuchong@gmail.com} \\
    GitHub: & \url{https://github.com/yuchong-pan}
  \end{tabular}
\end{minipage}


\section*{Personal}

\begin{itemize}
    \item Born on March 21, 1998.

    \item People's Republic of China Citizen.
\end{itemize}


\section*{Education}

\begin{itemize}
  \item Bachelor of Science, University of British Columbia, 2017-- .\\
  \emph{Gap year from May 2016 to August 2017.}

  \item Shaoxing No. 1 High School, 2013--2016.
\end{itemize}


\section*{Employment}

\begin{itemize}
  \item Co-Founder, Executive Board Member \& Director of Tech Department, hack.init(), 2017-- .\\
  \emph{Co-Founded the hack.init() hackathon, which aims to be China's premier youth hackathon. Working on management, tech support, corporate relations, recruitment, etc. Sole developer of the event's website }\url{http://hackinit.io}{.}

  \item Full-Stack Software Engineer (Internship), InitialView, 2016-- .\\
  \emph{Working on the front-end, back-end and mobile apps. Helping build and maintain InitialView's homepages, booking system, student portal, mobile apps, etc.}
\end{itemize}


\section*{Projects}

\begin{itemize}
  \item Viso, 2017.\\
  \emph{A coding interview platform with Leap Motion anti-cheating system, available at }\url{https://github.com/yuchong-pan/viso}\emph{. I designed the entire architecture of the web server and implemented the front-end and the back-end.}

  \item Aquatopia, 2017.\\
  \emph{A monitoring, alerting and visualization system for environmental data, available at }\url{https://devpost.com/software/aquatopia}\emph{ and at }\url{https://github.com/ShaolinZhang/aquatopia}\emph{. I designed the entire architecture of the web server and implemented the front-end and the back-end.}

  \item Hack Search, 2016.\\
  \emph{A field-specific (vertical), distributed search engine, available at }\url{https://github.com/joway/HackSearch}\emph{. I designed and implemented the front-end.}

  \item e-word, 2012--2013.\\
  \emph{A software program for English vocabulary memorizing, available at }\url{http://pan.baidu.com/share/link?shareid=482913&uk=355930340}\emph{. I designed and implemented the entire program.}

\end{itemize}


\section*{Awards}

\begin{itemize}
  \item Top 2, HackNanjing, 2017.

  \item Outstanding International Student Award, University of British Columbia, 2017.

  \item Top 9 and InnoSpring Award, HACKxFDU hackathon, 2016.

  \item Silver Medal, International Olympiad in Informatics China Team Selection Competition, 2015.

  \item Bronze Medal, Asia Pacific Informatics Olympiad, 2015.

  \item Top 500, Google Code Jam, 2015.

  \item Top 1000, Microsoft Beauty of Programming Challenge, 2014 \& 2015.

  \item First Prize, National Olympiad in Informatics in Provinces, 2013 \& 2014.

  \item Second Prize, National Olympiad in Informatics in Provinces, 2011 \& 2012.
\end{itemize}


\section*{Certificates}

\begin{itemize}
  \item Programming Ability Test (Advanced), Zhejiang University, Score 100/100, Rank 1/532.\\
  \emph{The introduction to Programming Ability Test can be found at }\url{https://www.patest.cn/p/articles?id=50}\emph{.}

  \item TOEFL iBT Test, Score 96/120.

  \item IELTS Test, Score 7.0/9.0.

  \item SAT Test, Reading 600/800, Mathematics 800/800, Writing 720/800, Essay 11/12.

  \item Advanced Placement Exams, Calculus BC 5/5, Statistics 5/5, Computer Science A 5/5.

  \item Certificate of Arts Grade Examination of China, Violin, Grade 10.
\end{itemize}


\section*{Experience}

\begin{itemize}
  \item Participant, HackNanjing hackathon, 2017.

  \item Participant, PennApps hackathon at University of Pennsylvania, 2017.

  \item Participant, HACKxFDU hackathon at Fudan University, 2016.

  \item Private English Tutor, 2016.

  \item Propositional Person of ACM-ICPC Multi-University Training Contests, Hangzhou Dianzi University Online Judge System, 2014.

  \item Student Lecturer of Olympiad in Informatics, Shaoxing No. 1 High School, 2013--2016.
 
  \item Propositional Person of Olympiad in Informatics Training Contests, Shaoxing No. 1 High School, 2013--2016.
\end{itemize}


\section*{Community Service}

\begin{itemize}
  \item Volunteer Guide, Shaoxing Luxun Native Place, 2015.

  \item Volunteer at the Radiological Department, Shaoxing People's Hospital, 2014.

  \item Volunteer of Emergency Medical Treatment, Shaoxing People's Hospital, 2013.
    
\end{itemize}


\section*{Languages}

\begin{itemize}
  \item C, C++, Java, Python, Pascal, Matlab, Octave, Racket, Scheme, Standard ML, Go, JavaScript, HTML, \LaTeX.
  \item Chinese (Mandarin), English.
\end{itemize}


\section*{Skills}

\begin{itemize}
  \item Full-Stack Web Development: Django, Flask, Tornado, HTML/CSS, JavaScript, Bootstrap, Vue.js, AngularJS, D3.js.

  \item App Development: Ionic, Delphi.

  \item Infrastructure: Nginx, Unix, Docker.

  \item Other: Team Leadership, Corporate Relations, Marketing & Public Relations.
\end{itemize}

\section*{Courses}

\begin{itemize}
  \item Machine Learning, Stanford University, Coursera.\\
  \emph{Completed the course with a final grade of $100.0\%$.}

  \item Programming Languages (Part A), University of Washington, Coursera.\\
  \emph{Completed the course with a final grade of $98.6\%$.}
\end{itemize}


\bigskip

% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%    %\href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
%\end{center}

\end{document}

