%-------------------------
% Resume in Latex
% Author : Yuchong Pan
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\awardSubItem}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://ypan.me/}{\Large Yuchong Pan}} & Email : \href{mailto:panyuchong@gmail.com}{panyuchong@gmail.com}\\
  \href{http://ypan.me/}{http://ypan.me} & Mobile : +1-604-782-7439 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of British Columbia}{Vancouver, BC}
      {Bachelor of Science}{September 2017 - May 2021 (Estimated)}
      \resumeSubHeadingListStart
          \resumeSubItem{Relevant Coursework}
            {Systematic Program Design; Models of Computation; Software Construction}
      \resumeSubHeadingListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Microsoft}{Vancouver, BC}
      {Garage Intern}{May 2018 - August 2018}

    \resumeSubheading
      {Sogou Inc.}{Beijing, China}
      {Software Engineer Intern}{May 2017 - July 2017}
      \resumeItemListStart
        \resumeItem{Speech-Recognition \& OCR Proofreading Tools}
          {Service for internal proofreading and testing of AI-Cloud services; using Bootstrap, Vue.js, Flask and Docker.}
        \resumeItem{Fapiao (Invoice) Recognition Service}
          {Service for Fapiao (invoice) format and content recognition; using Flask and scikit-image; based on Sogou AI-Cloud OCR API; used for reimbursements of Sogou's financial department.}
      \resumeItemListEnd

    \resumeSubheading
      {hack.init()}{Shanghai, China}
      {Co-Founder, Executive Board Member \& Director of Tech Department}{February 2017 - Present}
      \resumeItemListStart
        \resumeItem{hack.init() Hackathon 2017}
          {China's premier youth hackathon; July 8 to 9 at ShanghaiTech University; website at \url{http://hackinit.io}; press coverage at \url{https://goo.gl/ZFX3Ni} and \url{https://goo.gl/QXx8HM} (Simplified Chinese).}
        \resumeItem{Management}
          {Co-founded the hackathon; negotiated sponsorships from big corporations, including Google, Apple, Sogou and Wolfram, venture capitals and incubators; controlled main direction of the event.}
        \resumeItem{Technology}
          {Sole developer of event website; developed front-end and back-end; maintained server.}
      \resumeItemListEnd

    \resumeSubheading
      {InitialView}{Beijing, China}
      {Software Engineer Intern}{September 2016 - Present}
      \resumeItemListStart
        \resumeItem{Web Development}
          {Developed internal back-end API; developed front-end of InitialView's booking system, student portal, admissions portal and interview player; refactored InitialView's homepage.}
        \resumeItem{App Development}
          {Developed InitialView's mobile app on iOS and Android.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Vox}
      {A tool that redefines information structure for audio documents, with visualization and vertical search; based on Django; 1st Place at i-Lab Hackathon 2017.}
    \resumeSubItem{GitArt}
      {A GitHub-like idea-sharing and collaboration platform for artists, based on Django; Best Hack of Innovation at Unique Hackday 2017.}
    \resumeSubItem{Viso}
      {A coding interview platform with hardware anti-cheat system; based on Flask and Leap Motion; 2nd Place at Hack\{Nanjing\} 2017.}
    \resumeSubItem{Aquatopia}
      {A monitoring, alerting and visualization system for environmental data; based on Django; project at PennApps XV.}
    \resumeSubItem{HackSearch}
      {A vertical, distributed search engine; based on Elasticsearch, D3.js and Golang; Top 9 and InnoSpring Award at HACKxFDU 2016.}
  \resumeSubHeadingListEnd

%-----------Awards-----------------
\section{Awards}
  \resumeSubHeadingListStart
    \awardSubItem{11th Place, ACM International Collegiate Programming Contest Pacific NW Region}{November 2017}
    \awardSubItem{1st Place, Microsoft College Code Competition}{September 2017}
    \awardSubItem{1st Place, i-Lab Hackathon}{June 2017}
    %\awardSubItem{2nd Place, Hack\{Nanjing\}}{May 2017}
    \awardSubItem{Outstanding International Student Award, University of British Columbia}{February 2017}
    \awardSubItem{Silver Medal, China Team Selection Competition}{May 2015}
    \awardSubItem{Bronze Medal, Asia Pacific Informatics Olympiad}{May 2015}
    \awardSubItem{First Prize, National Olympiad in Informatics in Provinces}{November 2013}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {C++, Python, Java, Ruby, MATLAB, Racket, Go, JavaScript, MySQL, HTML, \LaTeX} \\
    \resumeSubItem{Technologies}
      {Django, Flask, Tornado, Microservices, Bootstrap, Vue.js, AngularJS, D3.js, Node.js, Marko.js, Ionic, Nginx, Redis, Docker} \\
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
